---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


### plots ESStream
## plot       <- x = time, y = hr & pace, facet = session
## plot_route <- x = long, y = lat, color = Speed, bkg <- stamen maps (ggmap)
## animacion <- single ride y multiride
## map facets
## map minimal 
## heatmap    <- x = long, y = lat, color = point density, bkg <- terrain map (ggmap)
## elev_prf   <- x = time, y = elevation, group = session, facets = session
## leaflet    <- single or multiple sessions
## summary    <- x = time, y = hr, speed, dist, duration etc, group = moving (or resting or total)
## timelin    <- x = time, y = Date
## dow        <- x = time, y = dow (geom ridges)
## training calendar






########## leaflet #####

# 
# 
# 
# leaflet() %>%
#   addTiles() %>%  # Add default OpenStreetMap map tiles
#   addCircleMarkers(data = dat_int, radius = 2, col = "red")
# 
# leaflet(dat) %>%
#   addTiles() %>%  # Add default OpenStreetMap map tiles
#   addCircleMarkers(radius = 5, color = (dat$tramo)) %>%
#   addMarkers(lng=javier_pochoco$lng[nrow(javier_pochoco)], lat=javier_pochoco$lat[nrow(javier_pochoco)], popup="inicio tramo") 
# 
# 
# crs_utm <- "+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
# crs_ll <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
# 
# 
# 
# muestra = base[sample(1:125367,70000,FALSE),]
# 
# 
# pal <- colorNumeric(
#   palette = terrain.colors(10),
#   domain = muestra$altitude)
# 
# 
# m <- leaflet(muestra) %>%
#   addTiles(group = "OSM (default)") %>%  # Añade por defecto los Tiles de  OpenStreetMap
#   addProviderTiles(providers$Stamen.Toner, group = "Toner") %>%
#   addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
#   addProviderTiles(providers$Esri.WorldImagery, group = "Satellite")%>%
#   addCircleMarkers(
#     radius = 1,
#     color =  ~pal(altitude),
#     stroke = FALSE, fillOpacity = 0.5
#   )  %>% addMarkers(lng=center_lng, lat=center_lat, popup="Plaza Manantiales")
# 
# 
# 
# 
# 
# ###########  ggplot ########## 
# 
# 
# ggmap(map) + geom_point(data=segs,shape=".",col="yellow",aes(lng,lat)) +
#   geom_polygon(data=shape.points,aes(long,lat,group=group,fill=Distancia_minima),color=NA,alpha=0.7) +
#   scale_fill_gradientn(colours = terrain.colors(3)) + 
#   geom_path(data=puntos_contorno,  aes(lng,lat, group=linea),col="red") +
#   geom_point(data=cerros,shape=17,col="darkgreen",aes(lng,lat),size=4) + 
#   labs(title = "Acceso a la Montaña #runtothehills", size=2,
#        subtitle = "Distancia (km) de cada manzana al cerro mas cercano", 
#        caption = "Fuentes: \n Stamen (mapa) \n SRTM (curvas de nivel) \n Wikiexplora, Andeshandbook, Strava (trayectorias cerros) \n  Tageo, Wikipedia, Geonames (coordenadas cumbres) \n 
#        Autor: Raimundo Sanchez, PhD")
# 
# get_density <- function(x, y, ...) {
#   dens <- MASS::kde2d(x, y, ...)
#   ix <- findInterval(x, dens$x)
#   iy <- findInterval(y, dens$y)
#   ii <- cbind(ix, iy)
#   return(dens$z[ii])
# }
# 
# require(ggimage) 
# 
# muestra_plot$density <- get_density(muestra_plot$lat, muestra_plot$lon, n = 100)
# 
# img = "desert-map-copy.jpg"
# 
# 
# p <- ggplot(muestra_plot) + 
#   geom_point(aes(lon, lat, col = density), size=1) + 
#   scale_color_gradient(low = "yellow", high = "red") +
#   ylim(-11.699,-11.6293) + 
#   xlim(166.8844,167.0253) +
#   theme_void() + 
#   theme(legend.position = "none")
# 
# png("watopia.png",units="px", width=700 , height=460)
# 
# ggbackground(p, img, alpha=.2) + 
#   ggtitle("   MAPA DE CALOR: WATOPIA", 
#           subtitle = "    ¿Por donde pedalea la comunidad Human Power?                        ROJO: alto trafico       AMARILLO: bajo trafico \n") + 
#   labs(caption = "Fuente: HumanPower.App    \n")
# 
# dev.off()
# 
# 
# # Create plot
# p <- ggplot() +
#   geom_density_ridges(aes(x = time, y = wday), plot_data, size = 0.5) +
#   theme_ridges() +
#   scale_y_discrete(expand = c(0.01, 0), labels = c("Sun", "Sat", "Fri", "Thu", "Wed", "Tue", "Mon")) +
#   scale_x_datetime(expand = c(0, 0), date_labels = "%I:%M %p") +
#   theme(panel.grid = element_blank(), plot.margin = unit(rep(1, 4), "cm")) +
#   xlab(NULL) + ylab(NULL)
# 
# # obtener distancias, default es en kms
# temp <- dplyr::group_by(temp, activity) %>%
#   dplyr::mutate(distance = get_dists(lon, lat)) %>% 
#   dplyr::ungroup()
# 
# ## defino margen de mapa (% del cuadrado generado por coordenadas)
# f = 0.05
# bbox <- ggmap::make_bbox(temp$lon, temp$lat, f = f)
# 
# ## generar mapa base zoom 13 es bien detallado, ahi jugar con ese parametro
# maptype = 'terrain'
# map <- suppressWarnings(suppressMessages(ggmap::get_map(bbox, maptype = maptype,zoom=13)))
# ## genera objeto de ggplot con mapa de fondo
# pbase <- suppressMessages(ggmap::ggmap(map) +
#                             ggplot2::coord_map() + 
#                             ggplot2::theme(axis.title = ggplot2::element_blank()))
# 
# ## agrega trayectorias de strava al mapa base
# p = pbase +
#   ggplot2::geom_path(ggplot2::aes(lon, lat, group = activity),
#                      data = temp,
#                      alpha = 1, size = .8, lineend = "round", colour = "red3") + ggplot2::ggtitle("Mapa Strava")
# 
# 
# 
# ########## stravalib ########## 
# 
# #' Plots activities superimposed on a map
# #'
# #' Plots activities superimposed on a map
# #' @param data A data frame output from process_data()
# #' @param lon_min Minimum longitude
# #' @param lon_max Maximum longitude
# #' @param lat_min Minimum latitude
# #' @param lat_max Maximum latitude
# #' @keywords
# #' @export
# #' @examples
# #' plot_map()
# 
# plot_map <- function(data, lon_min = -180, lon_max = 180, lat_min = -90, lat_max = 90) {
#   # Create plot
#   p <- ggplot2::ggplot() +
#     ggplot2::geom_path(ggplot2::aes(lon, lat, group = id),
#                        data %>% dplyr::filter(lon > lon_min, lon < lon_max, lat > lat_min, lat < lat_max),
#                        alpha = 0.3, size = 0.3, lineend = "round") +
#     ggplot2::coord_map() +
#     ggplot2::theme_void()
#   
#   # Return plot
#   p
# }
# 
# 
# 
# ########## animation ########## 
# 
# ### BACKYARD
# library(dplyr)
# library(rStrava)
# #library(gganimate)
# library(lubridate)
# #https://padpadpadpad.github.io/post/animate-your-strava-activities-using-rstrava-and-gganimate/
# 
# my_acts <- get_activity_list(stoken)
# external_id %like% "garmin_push_##"
# 
# f = 0.05
# bbox <- ggmap::make_bbox(temp$lon, temp$lat, f = f)
# 
# expand = 10
# 
# 
# maptype = 'terrain'
# map <- suppressWarnings(suppressMessages(ggmap::get_map(bbox, maptype = maptype,zoom=13,source="google")))
# 
# pbase <- suppressMessages(ggmap::ggmap(map) +
#                             ggplot2::coord_map() + 
#                             ggplot2::theme(axis.title = ggplot2::element_blank()))
# 
# 
# ventana_movil_dias = 90
# dia_inicio = as.Date("2014-12-01")
# frames = round(as.numeric(today() - dia_inicio)/7)
# super_temp = NULL
# 
# for (semana in 1:frames)
# {
#   
#   act_data <- compile_activities(my_acts) %>% 
#     filter(start_latitude <= -33.3 & start_latitude >= -33.45) %>%  
#     filter(start_longitude < -70.45 & start_longitude > -70.62)  %>% 
#     filter(as.Date(substr(start_date_local,1,10),"%Y-%m-%d") > dia_inicio+(semana-1)*7 - ventana_movil_dias & 
#              as.Date(substr(start_date_local,1,10),"%Y-%m-%d") < dia_inicio+(semana-1)*7 )
#   
#   act_data <- chk_nopolyline(act_data)
#   
#   temp <- dplyr::group_by(act_data, map.summary_polyline) %>%
#     dplyr::do(get_latlon(.)) %>%
#     dplyr::ungroup()
#   temp$activity <- as.numeric(factor(temp$map.summary_polyline))
#   temp$map.summary_polyline <- NULL
#   
#   
#   temp <- split(temp, temp$activity)
#   temp <- lapply(temp, function(x) {
#     
#     xint <- stats::approx(x = x$lon, n = expand * nrow(x))$y
#     yint <- stats::approx(x = x$lat, n = expand * nrow(x))$y
#     data.frame(activity = unique(x$activity), lat = yint, lon = xint)
#     
#   })
#   temp <- do.call('rbind', temp)
#   
#   # get distances, default is km
#   temp <- dplyr::group_by(temp, activity) %>%
#     dplyr::mutate(distance = get_dists(lon, lat)) %>% 
#     dplyr::ungroup()
#   
#   # xy lims
#   
#   #function(act_data, alpha = NULL, f = 1, key = NULL, add_elev = FALSE, as_grad = FALSE, distlab = TRUE, distval = 0, size = 0.5, col = 'red', expand = 10, maptype = 'terrain', source = 'google', ...)
#   temp$frame = dia_inicio+(semana-1)*7
#   super_temp = rbind(super_temp,temp)
#   
#   
# }
# 
# p2 = pbase +
#   ggplot2::geom_path(ggplot2::aes(lon, lat, group = frame),
#                      data = sample,
#                      alpha = 1, size = .8, lineend = "round", colour = "red3") +
#   transition_states(frame,transition_length = 3, state_length = 4,wrap=F) #+ view_follow() 
# 
# 
# anim2 <- animate(p2,fps = 20, duration = 30, width= 1024,  height=768) ## end_pause = 10, rewind = TRUE,
# anim_save("filenamehere.gif", anim2)
# 
# 
# anim2
# 
# 
# 
# 
# 
# p = 
#   
#   pbase +
#   ggplot2::geom_path(ggplot2::aes(lon, lat, group = activity),
#                      data = sample,
#                      alpha = 1, size = .8, lineend = "round", colour = "red3") + ggplot2::ggtitle({frame}) + 
#   transition_states(frame,transition_length = 4, state_length = 2) +
#   view_follow() + shadow_mark()
# 
# 
# 
# anim <- animate(p)
# anim_save("filenamehere.gif", anim)
# 
# 
# 
# sample = super_temp[super_temp$activity %in% 1,]
# 
# 
# 
# 
# anim_save("filenamehere.gif", anim2)
# 
# 
# 
# dev.copy(gif,paste0("/GIF/","year",".png"),width = 1024, height = 768)
# dev.off()
# print(nrow(act_data))
# print(year)
# 
# #all 412
# 
# #15 2014
# #121 2015
# #111 2016
# #46 2017
# #107 2018
# #12 2019
# 
# 



```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
