---
title: "GPS STREAM"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Abstract

This is a public use R library for data analysis of sports courses.You can find functions to load the data, pre-process it, correct the elevation and elevation gain of a route, and much more. ( C among others ). For data capture we use the library of _rStava_. <https://github.com/fawda123/rStrava>

Esta es una librería de uso público para análisis de datos de recorridos deportivos. Se podrán encontrar funciones para cargar los datos, procesarlos, corregir la elevación de un recorrido, entre otros. (AGREGAR FUNCIONES MÁS IMPORTANTES). Para la captura de datos se utilizo la librería de _rStrava_. <https://github.com/fawda123/rStrava>

### Overview and installation

This is the development repository for GPS_stream, an R package to analyze data from a GPS stream. The package can be installed and loaded as follows:

```{r message=FALSE, eval=FALSE}
install.packages('devtools')
devtools::install_github('raimun2/GPStream')
```

### Package overview

All the functions use **_data_**, that is a dataframe of a 'stream' that must have, time, elevation, lan and lon, etc. You can have it from _rStrava_ or *otro link que no me acurdo*. This package has an example data file named _data.R_ . For more information about how get a data file go to <https://github.com/fawda123/rStrava>


## GET_DATA

You can include R code in the document as follows:

```{r}


```

## Pre-processing the data
Ones you have the dataframe stream, the first step is pre-processing the stream to use all the function without failure. To do this, use the function _rename_stream_. Basically, the function search for typical names for the variables time, elevation, lon and lat. And change it for representative names to use the data in all functions of the library.

```{r message=FALSE, eval=FALSE}

data_stream <- rename_stream(data)

```

```{r cars, echo=FALSE}
summary(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
